---
title: "Factors Influencing Epidemic Outcomes"
author: "Chris Jones"
date: "5/4/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

	
The goal of this simulation study is to determine which factors have the greatest influence on epidemic outcomes. Here we are explicitly dividing the factors into two distinct categories: 1) disease ecology and 2) landscape structure. Once all of the 

## Glossary:
R0 = basic reproduction number\
P0 = initial population size\
B = Beta (simulation parameter for # spores dispersing per unit time under optimal conditions)\
LP = latent period\
IP = infectious period\
TA = treatment area (i.e. buffer around infected cell)\
TT = treatment timing\
HR =  host removal percentage\
PE = pesticide efficacy (pesticide is used to encompass (vaccinations, fungicides, pesticides, etc..)\
PD = pesticide duration (how many time units does the pesticide provide resistance)
DD = Dispersal kernel scale parameter 

## Experimental Setup
Run all simulations on a 200 x 200 area. We are keeping total amount of host constant but varying spatial arrangement.
Run out for 80 time units (5 generations).

### Factorial of Lifecycle Factors (1280 combinations)
5 B = (1.25, 2, 4, 8, 16)\
3 P0 = (1, 10, 20) % infection at the epidemic outbreak\
4 LP = (2, 4, 8, 16)\
3 IP = (0.5, 1, 1.5 x LP)\
3 DD = (2.1, 10, 20)

### Add in Landscape complexity (9)
3 LP = (Uniform, random, clumped)\
3 HA = (10, 30, 50 percent of the total area)

### Add in treatment effects (16 * 6 = 96)
#### Timing and size effects (16 combinations)
4 TT = (1.5, 2.0, 2.5, 3.0 x LP)\
4 TA = (1, 3, 5, 7 x cell size)

#### Vaccination/Pesticide/Fungicide and host removal effects (6 options)
3 PE = (0.95, 0.75, 0.50)\
3 HR = (1.00, 0.75, 0.50 in TA but always 1.00 in infected cell)\
1 PD = 24 days

Total Factorial Combinations = 466,560 


```{r landscapes}

```



```{r plots, echo=FALSE}

```

